An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Added comments on Section 4

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}

@@

  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
\end{proof}

@@

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, the link function $\psi$ is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
Thus, our framework would have simplified the process of finding such a link function.

>>>>

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
\jessie{It might help to say something like: initialize a \emph{potential link} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$, or something to explain what $\Psi$ is?  (Note sure how to phrase it.)}

@@

  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
\end{proof}
\jessie{Should be add a note that the full proof is given in the Appendix?}

@@

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, the link function $\psi$ \jessie{changed from $\Psi$?} is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
We show the full construction of $\psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
Thus, our framework would have simplified the process of finding such a link function.
